Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle Structure

### 2017-06-19 documents/TriangleScenarioArXiv/ts.tex
Changed A2 again

    \begin{figure}
    \begin{center}
        \begin{minipage}[t]{.48\textwidth}
            \centering
            \scalebox{1.0}{\input{../../figures/causal_structures/bell_scenario}}
            \caption{The Bell structure consisting of two observers $\p{A}, \p{B}$ together with measurement settings $S_{\p{A}}$ and $S_{\p{B}}$ respectively. The shared hidden variable is labeled $\la$.}
            \label{fig:bell_structure}
        \end{minipage}\hspace{0.04\textwidth}%
        \begin{minipage}[t]{.48\textwidth}
            \centering
            \scalebox{1.0}{\input{../../figures/causal_structures/triangle_structure}}
            \caption{The casual structure of the Triangle structure. Three variables $A,B,C$ are observable, while $X, Y, Z$ are latent variables.}
            \label{fig:triangle_structure}
        \end{minipage}
    \end{center}
    \end{figure}
    \section{Triangle structure}
    \label{sec:triangle_structure}

@@

    \section{Fritz Distribution}
    \label{sec:fritz_distribution}
    \begin{figure}
    \begin{center}
        \scalebox{1.0}{\input{../../figures/causal_structures/triangle_structure_operational_fritz_bell}}
        \caption{The Triangle structure re-imagined to mimic the Bell structure. The measurement settings $S_{\p{A}},S_{\p{B}}$ are latent nodes unlike the Bell structure (\cref{fig:bell_structure}).}
        \label{fig:triangle_structure_with_fritz_bell_embedded}
    \end{center}
    \end{figure}

@@

    \begin{center}

@@

    \end{center}

@@

    The first causal compatibility inequality chosen for presentation is reported below:
    \begin{equation*}
    \begin{gathered}
    \eq\label{eq:ww_ineq}
    I\tsb{WagonWheel} : \\
    + P_{ABC}(000)P_{C}(3) - 2P_{ABC}(203)P_{C}(0) - 2P_{ABC}(303)P_{C}(0) - P_{ABC}(003)P_{C}(0) \\
    - P_{ABC}(013)P_{C}(0) - P_{ABC}(020)P_{C}(2) - P_{ABC}(022)P_{C}(2) - P_{ABC}(023)P_{C}(0) \\
    - P_{ABC}(023)P_{C}(2) - P_{ABC}(030)P_{C}(2) - P_{ABC}(031)P_{C}(2) - P_{ABC}(032)P_{C}(2) \\
    - P_{ABC}(033)P_{C}(0) - P_{ABC}(033)P_{C}(2) - P_{ABC}(103)P_{C}(0) - P_{ABC}(113)P_{C}(0) \\
    - P_{ABC}(123)P_{C}(0) - P_{ABC}(133)P_{C}(0) - P_{ABC}(200)P_{C}(0) - P_{ABC}(200)P_{C}(1) \\
    - P_{ABC}(200)P_{C}(2) - P_{ABC}(200)P_{C}(3) - P_{ABC}(201)P_{C}(0) - P_{ABC}(201)P_{C}(1) \\
    - P_{ABC}(201)P_{C}(2) - P_{ABC}(201)P_{C}(3) - P_{ABC}(203)P_{C}(1) - P_{ABC}(203)P_{C}(2) \\
    - P_{ABC}(203)P_{C}(3) - P_{ABC}(213)P_{C}(0) - P_{ABC}(223)P_{C}(0) - P_{ABC}(300)P_{C}(0) \\
    - P_{ABC}(300)P_{C}(1) - P_{ABC}(300)P_{C}(2) - P_{ABC}(300)P_{C}(3) - P_{ABC}(301)P_{C}(0) \\
    - P_{ABC}(301)P_{C}(1) - P_{ABC}(301)P_{C}(2) - P_{ABC}(301)P_{C}(3) - P_{ABC}(302)P_{C}(1) \\
    - P_{ABC}(303)P_{C}(1) - P_{ABC}(303)P_{C}(2) - P_{ABC}(303)P_{C}(3) - P_{ABC}(313)P_{C}(0) \leq 0
    \end{gathered}
    \end{equation*}
    \Cref{eq:ww_ineq} is termed the Wagon Wheel inequality and denoted $I\tsb{WagonWheel}$ after the identically named inflation (\cref{fig:wagon_wheel_inflation}) utilized to derive it. To reiterate, a summary of the methods used to derive \cref{eq:ww_ineq} can be found in \cref{sec:marginal_satisfiability,sec:inflation_technique_main_summary,sec:exemplary_inflations_of_the_triangle_structure}.

@@

    \subsection{Noisy Distributions}
    \label{sec:noise}
    % \begin{figure}
    % \begin{center}
    %         \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{../../figures/distributions/uniform_dist_plot.pdf}
    %         \vspace{-0.2in}
    %         \[ \probplotvalue{255, 255, 109} = \f{1}{64} \]
    %         \caption{The completely uniform distribution $\s{U}$ visualized using a $4 \times 4 \times 4$ grid.}
    %         \label{fig:uniform_distribution}
    % \end{center}
    % \end{figure}
    In his original work, \citet{Fritz_2012} was able to find quantum non-classicality in the Triangle structure by embedding Bell non-classicality. As was mentioned in \cref{sec:fritz_distribution}, this embedding required an idealistic condition to hold: perfect correlations between $C$ and $A_l, B_l$. From an experimental point of view, it is impossible to use Fritz's original argument to confirm non-classicality because every observable distribution is subject to \text{noise}. It is possible to minimize noise by developing more accurate measurement channels but perfect correlations are too idealistic. Causal compatibility inequalities not only permit there to be noise within a set of observations, but they also provide a means of quantifying the amount of noise that is allowed before non-classicality breaks down.

@@

    \begin{figure}
    \begin{center}
            \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{../../figures/noise/noisy_yet_non_local_fritz.pdf}
            \vspace{-0.2in}
            \[ \probplotvalue{255, 255, 243} = 0.00133 \]
            \caption{$\s{N}_{0.085}$: A noisy yet still non-classical variant of the Fritz distribution.}
            \label{fig:noisy_fritz}
    \end{center}
    \end{figure}

@@

    % \subsection{Parameterizing Quantum Distributions}
    % \begin{figure}
    % \begin{center}
    %         \scalebox{1.0}{\input{../../figures/causal_structures/triangle_structure_operational}}
    %         \caption{The Triangle structure as modeled by quantum states and measurements.}
    %         \label{fig:triangle_structure_quantum_model}
    % \end{center}
    % \end{figure}

@@

    \begin{figure}
    \begin{center}
            \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{../../figures/distributions/plotted_dist_I_1_max_violation_2017.pdf}
            \caption{Probability distribution that maximizes violation of $I\tsb{Web}$ ($V_F \simeq 1.501$).}
            \label{fig:maximum_violation_I_1}
    \end{center}
    \end{figure}
    \begin{figure}
    \begin{center}
            \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{../../figures/distributions/plotted_dist_I_3_max_violation_2017.pdf}
            \caption{Probability distribution that maximizes violation of $I\tsb{SymmetricWeb}$ ($V_F \simeq 2.61$).}
            \label{fig:maximum_violation_I_3}
    \end{center}
    \end{figure}
    \begin{figure}
    \begin{center}
            \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{../../figures/distributions/symmetrized_fritz.pdf}
            \caption{Symmetrized version of the Fritz distribution ($V_F \simeq 3$).}
            \label{fig:symmetrized_fritz}
    \end{center}
    \end{figure}

@@

    Each of the above mentioned techniques suffers from computational complexity limitations. For example, the Fourier-Motzkin procedure is in the worst case doubly exponential in the number of initial inequalities~\cite{Dantzig_1973}. For the purposes of this research, solving the marginal problem without reference to a marginal model was intractable. This will become apparent in \cref{sec:exemplary_inflations_of_the_triangle_structure} when the Inflation Technique is applied to the Triangle structure, producing considerably large marginal models. Luckily, the Fritz distribution (\cref{sec:fritz_distribution}) allows one to avoid the complexity issues of the complete marginal problem and instead focus on the original problem of determining whether or not a particular marginal model admits a joint distribution or not.
    \subsection{Inflation Technique}
    \label{sec:deriving_inequalities}
    \label{sec:inflation_technique_main_summary}
    The \term{Inflation Technique}, invented by \citet{Inflation} and inspired by the \textit{do calculus} and \textit{twin networks} of \citet{Pearl_2009}, is a family of causal inference techniques that can be used to determine if an observable probability distribution $\prob[\nodes_{O}]$ is compatible or incompatible with a given causal structure $\graph$. As a precursor, the Inflation Technique begins by \textit{augmenting} a causal structure with additional copies of its nodes, producing an \textit{inflated} causal structure, and then exposes how causal inference tasks on the inflated causal structure can be used to make inferences on the original causal structure. As a example, a few inflations of the Triangle structure are depicted in \cref{fig:inflations}. Copies of nodes in the inflated causal structure are distinguished by an additional subscript called the \term{copy-index}. For example, node $A$ of \cref{fig:triangle_structure} has copies $A_1, A_2, A_3, A_4$ in the inflated causal structure in \cref{fig:the_web_inflation}. All such copies are deemed equivalent via a \term{copy-index equivalence} relation denoted `$\sim$'. A copy-index is effectively arbitrary, so we will refer to an arbitrary inflated copy of $A$ as $A'$.
    \[ A \sim A_1 \sim A' \not\sim B \sim B_1 \sim B' \]
    We preemptively generalize the notion of copy-index equivalence to other mathematical objects like sets, graphs, and groups by saying that $X \sim Y$ if and only if $X = Y$ upon removal of the copy-index. In addition to the common graph-theoretic terminology and notation presented in \cref{sec:causal_compatibility}, we define two more concepts necessary to formally define an inflation of $\graph$. First, an \term{induced subgraph} of $\graph$ for a subset of nodes $N \subseteq \nodes$ is another graph composed of nodes $N$ and all edges $e$ of the original graph that are contained in $N$: $\Sub[\graph]{N} \defined \br{N, \bc{e = \bc{n \to m} \mid n, m \in N}}$. An \term{ancestral subgraph} of $\graph$ for a subset of nodes $N \subseteq \nodes$ is the induced subgraph due to the ancestry of $N$: $\AnSub[\graph]{N} \defined \Sub[\graph]{\An[\graph]{N}}$.

    \begin{definition}
        \label{def:inflation}
        An \term{inflation} of a causal structure $\graph$ is another causal structure $\graph'$ such that:
        \[ \forall n' \in \nodes': \AnSub[\graph']{n'} \sim \AnSub[\graph]{n} \eq \label{eq:inflation_defn}\]
    \end{definition}
    \begin{center}
    \begin{figure}
    \begin{subfigure}[b]{.30\linewidth}
    \scalebox{0.65}{\input{../../figures/causal_structures/inflated_triangle_structure_spiral}}
    \caption{The Spiral inflation.}\label{fig:spiral_inflation}
    \end{subfigure}
    \begin{subfigure}[b]{.30\linewidth}
    \scalebox{0.65}{\input{../../figures/causal_structures/inflated_triangle_structure_wagon_wheel}}
    \caption{The Wagon-Wheel inflation.}\label{fig:wagon_wheel_inflation}
    \end{subfigure}
    \begin{subfigure}[b]{.30\linewidth}
    \scalebox{0.65}{\input{../../figures/causal_structures/inflated_triangle_structure}}
    \caption{The Web Inflation.}\label{fig:the_web_inflation}
    \end{subfigure}
    \caption{Some inflations of the Triangle structure.}
    \label{fig:inflations}
    \end{figure}
    \end{center}
    \begin{center}
    \begin{figure}
    \begin{subfigure}[b]{.23\linewidth}
    \scalebox{0.8}{\input{../../figures/causal_structures/inflated_triangle_structure_spiral_injectable_highlight_1}}
    \caption{$\AnSub[\graph']{A_1}$}\label{fig:spiral_inflation_inj1}
    \end{subfigure}
    \begin{subfigure}[b]{.23\linewidth}
    \scalebox{0.8}{\input{../../figures/causal_structures/triangle_structure_injectable_highlight_1}}
    \caption{$\AnSub[\graph]{A}$}\label{fig:spiral_inflation_iminj1}
    \end{subfigure}
    % \par\bigskip % For vertical spacing https://tex.stackexchange.com/questions/120700/vertical-spacing-using-subcaption-package
    \begin{subfigure}[b]{.23\linewidth}
    \scalebox{0.8}{\input{../../figures/causal_structures/inflated_triangle_structure_spiral_injectable_highlight_2}}
    \caption{$\AnSub[\graph']{A_2, C_1}$}\label{fig:spiral_inflation_inj2}
    \end{subfigure}
    \begin{subfigure}[b]{.23\linewidth}
    \scalebox{0.8}{\input{../../figures/causal_structures/triangle_structure_injectable_highlight_2}}
    \caption{$\AnSub[\graph]{A,C}$}\label{fig:spiral_inflation_iminj2}
    \end{subfigure}
    \caption{Some injectable sets $\Inj[\graph]{\graph'}$ of the Spiral inflation ($\graph'$) and their corresponding images $\ImInj[\graph]{\graph'}$ in the Triangle structure ($\graph$).}
    \label{fig:injectablesets}
    \end{figure}
    \end{center}
    For each inflated node $n'$, the ancestral sub-graph of $n'$ in $\graph'$ is homomorphic to its counterpart in $\graph$ where the homomorphism is the removal of the copy-index. For example, the ancestral subgraph of $A$ in the Triangle structure (denoted $\AnSub[\graph]{A}$) is highlighted in \cref{fig:spiral_inflation_iminj1} and is clearly homomorphic to the ancestral subgraph of $A_1$ in the Spiral inflation (denoted $\AnSub[\graph]{A_1}$) depicted in \cref{fig:spiral_inflation_inj1}. Since this ancestral homomorphism exists for each node $n'$ of the Spiral inflation (\cref{fig:spiral_inflation}), it qualifies as a valid inflation of the Triangle structure (\cref{fig:triangle_structure}).

    \begin{definition}
        Given a causal structure $\graph$ and an inflation $\graph'$ of $\graph$, define the \term{injectable sets} in $\graph'$ and the \term{images of the injectable sets} in $\graph$, (respectively denoted $\Inj[\graph]{\graph'}$ and $\ImInj[\graph]{\graph'}$), as follows:
        \begin{align*}
            \Inj[\graph]{\graph'} &\defined \bc{N' \subseteq \nodes' \mid \exists N \subseteq \nodes : \AnSub[\graph']{N'} \sim \AnSub[\graph]{N}} \\
            \ImInj[\graph]{\graph'} &\defined \bc{N \subseteq \nodes \mid \exists N' \subseteq \nodes' : \AnSub[\graph']{N'} \sim \AnSub[\graph]{N}}
        \end{align*}
    \end{definition}

    As an example of an injectable set, the set $\bc{A_2, C_1}$ of the Spiral inflation ($\graph'$) (\cref{fig:spiral_inflation}) is an injectable set of $\graph'$ because its ancestral subgraph $\AnSub[\graph']{A_2, C_1}$ (highlighted in \cref{fig:spiral_inflation_inj2}) is homomorphic (via copy-index removal) to the ancestral subgraph of $\bc{A, C}$ in the Triangle structure $(\graph)$ (\cref{fig:spiral_inflation_iminj2}). The injectable sets of an inflation are of \textit{principle importance} to the inflation technique. The Inflation Technique begins with joint distribution $\prob[\nodes_O]$ defined over the observable nodes of $\graph$ and the a priori assumption that it is compatible with $\graph$ as defined in \cref{sec:causal_compatibility}. For each injectable set $N' \subseteq \Inj[\graph]{\graph'}$ and image $N \subseteq \ImInj[\graph]{\graph'}$ consisting entirely of observable nodes ($N \subseteq \nodes_O$), there is a pair $\prob[N], \prob[N']$ of marginal distributions induced by $\prob[\nodes_O]$ where $\prob[N']$ assigns the same probability to all events of $\prob[N]$ whenever the events are equivalent under the removal of copy-indices. These pairs of distributions can be raveled to form a pair of marginal models defined over the injectable sets $\prob^{\Inj[\graph]{\graph'}} = \bc{\prob[N'] \mid N' \in \Inj[\graph]{\graph'}}$ and their images $\prob^{\ImInj[\graph]{\graph'}} = \bc{\prob[N] \mid N \in \ImInj[\graph]{\graph'}}$.

    \begin{lemma}
        \label[lemma]{lem:inflation}
        \term{The Inflation Lemma}~\cite[Lemma 3]{Inflation} Given a particular inflation $\graph'$ of $\graph$ and a marginal model $\prob^{\ImInj[\graph]{\graph'}}$ compatible with $\graph$ then all marginal models $\prob^{\Inj[\graph]{\graph'}}$ are compatible with $\graph'$ provided that $\prob[N] = \prob[N']$ for all instances where $N \sim N'$.
    \end{lemma}

>>>>

    \begin{figure}
    \begin{nscenter}
        \begin{minipage}[t]{.48\textwidth}
            \centering
            \scalebox{1.0}{\input{../../figures/causal_structures/bell_scenario}}
            \caption{The Bell structure consisting of two observers $\p{A}, \p{B}$ together with measurement settings $S_{\p{A}}$ and $S_{\p{B}}$ respectively. The shared hidden variable is labeled $\la$.}
            \label{fig:bell_structure}
        \end{minipage}\hspace{0.04\textwidth}%
        \begin{minipage}[t]{.48\textwidth}
            \centering
            \scalebox{1.0}{\input{../../figures/causal_structures/triangle_structure}}
            \caption{The casual structure of the Triangle structure. Three variables $A,B,C$ are observable, while $X, Y, Z$ are latent variables.}
            \label{fig:triangle_structure}
        \end{minipage}
    \end{nscenter}
    \end{figure}
    \section{Triangle structure}
    \label{sec:triangle_structure}

@@

    \section{Fritz Distribution}
    \label{sec:fritz_distribution}
    \begin{figure}
    \begin{nscenter}
        \scalebox{1.0}{\input{../../figures/causal_structures/triangle_structure_operational_fritz_bell}}
        \caption{The Triangle structure re-imagined to mimic the Bell structure. The measurement settings $S_{\p{A}},S_{\p{B}}$ are latent nodes unlike the Bell structure (\cref{fig:bell_structure}).}
        \label{fig:triangle_structure_with_fritz_bell_embedded}
    \end{nscenter}
    \end{figure}

@@

    \begin{nscenter}

@@

    \end{nscenter}

@@

    The first causal compatibility inequality chosen for presentation is reported below:
    \begin{equation*}
    \begin{gathered}
    \eq\label{eq:ww_ineq}
    I\tsb{WagonWheel} : \\
    + P_{ABC}(000)P_{C}(3) - 2P_{ABC}(203)P_{C}(0) - 2P_{ABC}(303)P_{C}(0) - P_{ABC}(003)P_{C}(0) \\
    - P_{ABC}(013)P_{C}(0) - P_{ABC}(020)P_{C}(2) - P_{ABC}(022)P_{C}(2) - P_{ABC}(023)P_{C}(0) \\
    - P_{ABC}(023)P_{C}(2) - P_{ABC}(030)P_{C}(2) - P_{ABC}(031)P_{C}(2) - P_{ABC}(032)P_{C}(2) \\
    - P_{ABC}(033)P_{C}(0) - P_{ABC}(033)P_{C}(2) - P_{ABC}(103)P_{C}(0) - P_{ABC}(113)P_{C}(0) \\
    - P_{ABC}(123)P_{C}(0) - P_{ABC}(133)P_{C}(0) - P_{ABC}(200)P_{C}(0) - P_{ABC}(200)P_{C}(1) \\
    - P_{ABC}(200)P_{C}(2) - P_{ABC}(200)P_{C}(3) - P_{ABC}(201)P_{C}(0) - P_{ABC}(201)P_{C}(1) \\
    - P_{ABC}(201)P_{C}(2) - P_{ABC}(201)P_{C}(3) - P_{ABC}(203)P_{C}(1) - P_{ABC}(203)P_{C}(2) \\
    - P_{ABC}(203)P_{C}(3) - P_{ABC}(213)P_{C}(0) - P_{ABC}(223)P_{C}(0) - P_{ABC}(300)P_{C}(0) \\
    - P_{ABC}(300)P_{C}(1) - P_{ABC}(300)P_{C}(2) - P_{ABC}(300)P_{C}(3) - P_{ABC}(301)P_{C}(0) \\
    - P_{ABC}(301)P_{C}(1) - P_{ABC}(301)P_{C}(2) - P_{ABC}(301)P_{C}(3) - P_{ABC}(302)P_{C}(1) \\
    - P_{ABC}(303)P_{C}(1) - P_{ABC}(303)P_{C}(2) - P_{ABC}(303)P_{C}(3) - P_{ABC}(313)P_{C}(0) \leq 0
    \end{gathered}
    \end{equation*}
    \Cref{eq:ww_ineq} is termed the Wagon Wheel inequality and denoted $I\tsb{WagonWheel}$ after the identically named inflation (\cref{fig:wagon_wheel_inflation}) utilized to derive it. To reiterate, a summary of the methods used to derive \cref{eq:ww_ineq} can be found in \cref{sec:marginal_satisfiability,sec:inflation_technique_main_summary,sec:deriving_inequalities_from_the_inflation_technique}.

@@

    \subsection{Noisy Distributions}
    \label{sec:noise}
    % \begin{figure}
    % \begin{nscenter}
    %         \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{../../figures/distributions/uniform_dist_plot.pdf}
    %         \vspace{-0.2in}
    %         \[ \probplotvalue{255, 255, 109} = \f{1}{64} \]
    %         \caption{The completely uniform distribution $\s{U}$ visualized using a $4 \times 4 \times 4$ grid.}
    %         \label{fig:uniform_distribution}
    % \end{nscenter}
    % \end{figure}
    In his original work, \citet{Fritz_2012} was able to find quantum non-classicality in the Triangle structure by embedding Bell non-classicality. As was mentioned in \cref{sec:fritz_distribution}, this embedding required an idealistic condition to hold: perfect correlations between $C$ and $A_l, B_l$. From an experimental point of view, it is impossible to use Fritz's original argument to confirm non-classicality because every observable distribution is subject to \text{noise}. It is possible to minimize noise by developing more accurate measurement channels but perfect correlations are too idealistic. Causal compatibility inequalities not only permit there to be noise within a set of observations, but they also provide a means of quantifying the amount of noise that is allowed before non-classicality breaks down.

@@

    \begin{figure}
    \begin{nscenter}
            \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{../../figures/noise/noisy_yet_non_local_fritz.pdf}
            \vspace{-0.2in}
            \[ \probplotvalue{255, 255, 243} = 0.00133 \]
            \caption{$\s{N}_{0.085}$: A noisy yet still non-classical variant of the Fritz distribution.}
            \label{fig:noisy_fritz}
    \end{nscenter}
    \end{figure}

@@

    % \subsection{Parameterizing Quantum Distributions}
    % \begin{figure}
    % \begin{nscenter}
    %         \scalebox{1.0}{\input{../../figures/causal_structures/triangle_structure_operational}}
    %         \caption{The Triangle structure as modeled by quantum states and measurements.}
    %         \label{fig:triangle_structure_quantum_model}
    % \end{nscenter}
    % \end{figure}

@@

    \begin{figure}
    \begin{nscenter}
            \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{../../figures/distributions/plotted_dist_I_1_max_violation_2017.pdf}
            \caption{Probability distribution that maximizes violation of $I\tsb{Web}$ ($V_F \simeq 1.501$).}
            \label{fig:maximum_violation_I_1}
    \end{nscenter}
    \end{figure}
    \begin{figure}
    \begin{nscenter}
            \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{../../figures/distributions/plotted_dist_I_3_max_violation_2017.pdf}
            \caption{Probability distribution that maximizes violation of $I\tsb{SymmetricWeb}$ ($V_F \simeq 2.61$).}
            \label{fig:maximum_violation_I_3}
    \end{nscenter}
    \end{figure}
    \begin{figure}
    \begin{nscenter}
            \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{../../figures/distributions/symmetrized_fritz.pdf}
            \caption{Symmetrized version of the Fritz distribution ($V_F \simeq 3$).}
            \label{fig:symmetrized_fritz}
    \end{nscenter}
    \end{figure}

@@

    Each of the above mentioned techniques suffers from computational complexity limitations. For example, the Fourier-Motzkin procedure is in the worst case doubly exponential in the number of initial inequalities~\cite{Dantzig_1973}. For the purposes of this research, solving the marginal problem without reference to a marginal model was intractable. This will become apparent in \cref{sec:deriving_inequalities_from_the_inflation_technique} when the Inflation Technique is applied to the Triangle structure, producing considerably large marginal models. Luckily, the Fritz distribution (\cref{sec:fritz_distribution}) allows one to avoid the complexity issues of the complete marginal problem and instead focus on the original problem of determining whether or not a particular marginal model admits a joint distribution or not.
    \subsection{Inflation Technique}
    \label{sec:deriving_inequalities}
    \label{sec:inflation_technique_main_summary}
    The \term{Inflation Technique}, invented by \citet{Inflation} and inspired by the \textit{do calculus} and \textit{twin networks} of \citet{Pearl_2009}, is a family of causal inference techniques that can be used to determine if an observable probability distribution $\prob[\nodes_{O}]$ is compatible or incompatible with a given causal structure $\graph$. As a precursor, the Inflation Technique begins by \textit{augmenting} a causal structure $\graph$ with additional copies of its nodes, producing an \textit{inflated} causal structure $\graph'$ called an \term{inflation}, and then exposes how causal inference tasks on the inflation can be used to make inferences on the original causal structure. For reference, a few inflations of the Triangle structure are depicted in \cref{fig:inflations}. Copies of nodes in the inflated causal structure are distinguished by an additional subscript called the \term{copy-index}. For example, node $A$ of \cref{fig:triangle_structure} has copies $A_1, A_2, A_3, A_4$ in the inflated causal structure in \cref{fig:the_web_inflation}. All such copies are deemed equivalent via a \term{copy-index equivalence} relation denoted `$\sim$'. A copy-index is effectively arbitrary, so we will refer to an arbitrary inflated copy of $A$ as $A'$, i.e. $A \sim A_1 \sim A' \not\sim B \sim B_1 \sim B'$.\footnote{Note that we preemptively generalize the notion of copy-index equivalence to other mathematical objects like sets, graphs, and groups by saying that $X \sim Y$ if and only if $X$ is equivalent to $Y$ upon removal of the copy-index.}

    \begin{nscenter}
    \begin{figure}
    \begin{subfigure}[b]{.30\linewidth}
    \scalebox{0.65}{\input{../../figures/causal_structures/inflated_triangle_structure_spiral}}
    \caption{The Spiral inflation.}\label{fig:spiral_inflation}
    \end{subfigure}
    \begin{subfigure}[b]{.30\linewidth}
    \scalebox{0.65}{\input{../../figures/causal_structures/inflated_triangle_structure_wagon_wheel}}
    \caption{The Wagon-Wheel inflation.}\label{fig:wagon_wheel_inflation}
    \end{subfigure}
    \begin{subfigure}[b]{.30\linewidth}
    \scalebox{0.65}{\input{../../figures/causal_structures/inflated_triangle_structure}}
    \caption{The Web Inflation.}\label{fig:the_web_inflation}
    \end{subfigure}
    \caption{Some inflations of the Triangle structure.}
    \label{fig:inflations}
    \end{figure}
    \end{nscenter}

    In addition to the common graph-theoretic terminology and notation presented in \cref{sec:causal_compatibility}, two related concepts need introductions. First, an \term{induced subgraph} of $\graph$ for a subset of nodes $N \subseteq \nodes$ is the graph composed of nodes $N$ and all edges $e$ of the original graph that are contained in $N$: $\Sub[\graph]{N} \defined \br{N, \bc{e = \bc{n \to m} \mid n, m \in N}}$. An \term{ancestral subgraph} of $\graph$ for a subset of nodes $N \subseteq \nodes$ is the induced subgraph due to the ancestry of $N$: $\AnSub[\graph]{N} \defined \Sub[\graph]{\An[\graph]{N}}$.

    The Inflation Technique begins with distribution $\prob[N]$ defined over some observable nodes $N$ of $\graph$ and the a priori assumption that it is compatible with $\graph$ pursuant to the definitions provided in \cref{sec:causal_compatibility}. Regarding $\graph$ as a causal hypothesis, the observable correlation $\prob[N]$ can only be influenced by the ancestry of $N$ in $\graph$. Consequently, for any set of nodes $N'$ of an inflation $\graph'$ where the ancestral subgraph $\AnSub[\graph']{N'}$ happens to be homomorphic to the ancestral subgraph $\AnSub[\graph]{N}$, one can conclude that the distribution $\prob[N']$ (induced by $\prob[N]$\footnote{The inflated distribution $\prob[N']$ assigns the same probability to all events of $\prob[N]$ whenever the events are equivalent under the removal of copy-indices.}) is compatible with $\graph'$ using the same latent explanations for $\prob[N]$ in $\graph$. This observation is known as the \term{Inflation Lemma}~\cite[Lemma 3]{Inflation}.

    To formalize the Inflation Lemma, we define the \term{injectable sets of $\graph'$}, denoted $\Inj[\graph]{\graph'}$, as all sets of nodes in $\graph'$ whose ancestral subgraphs are homomorphic (via copy-index removal) to an ancestral subgraph in $\graph$: $\Inj[\graph]{\graph'} \defined \bc{N' \subseteq \nodes' \mid \exists N \subseteq \nodes : \AnSub[\graph']{N'} \sim \AnSub[\graph]{N}}$. Analogously defined are the \term{images of the injectable sets in $\graph$}: $\ImInj[\graph]{\graph'} \defined \bc{N \subseteq \nodes \mid \exists N' \subseteq \nodes' : \AnSub[\graph']{N'} \sim \AnSub[\graph]{N}}$.

    To illustrate these concepts, consider the Spiral inflation $\graph'$ depicted in \cref{fig:spiral_inflation}. The ancestral subgraph of $\bc{A_1}$ in the Spiral inflation (denoted $\AnSub[\graph']{\bc{A_1}}$) is highlighted in \cref{fig:spiral_inflation_inj1} and is clearly homomorphic to the ancestral subgraph of its image $\bc{A}$ in the Triangle structure ($\graph$) (\cref{fig:spiral_inflation_iminj1}). Additionally, the set $\bc{A_2, C_1}$ is an injectable set of $\graph'$ because $\AnSub[\graph']{\bc{A_2, C_1}}$ (highlighted in \cref{fig:spiral_inflation_inj2}) is homomorphic (via copy-index removal) to the $\AnSub[\graph]{\bc{A, C}}$ in the Triangle structure $(\graph)$ (\cref{fig:spiral_inflation_iminj2}).

    \begin{nscenter}
    \begin{figure}
    \begin{subfigure}[b]{.23\linewidth}
    \scalebox{0.8}{\input{../../figures/causal_structures/inflated_triangle_structure_spiral_injectable_highlight_1}}
    \caption{$\AnSub[\graph']{\bc{A_1}}$}\label{fig:spiral_inflation_inj1}
    \end{subfigure}
    \begin{subfigure}[b]{.23\linewidth}
    \scalebox{0.8}{\input{../../figures/causal_structures/triangle_structure_injectable_highlight_1}}
    \caption{$\AnSub[\graph]{\bc{A}}$}\label{fig:spiral_inflation_iminj1}
    \end{subfigure}
    % \par\bigskip % For vertical spacing https://tex.stackexchange.com/questions/120700/vertical-spacing-using-subcaption-package
    \begin{subfigure}[b]{.23\linewidth}
    \scalebox{0.8}{\input{../../figures/causal_structures/inflated_triangle_structure_spiral_injectable_highlight_2}}
    \caption{$\AnSub[\graph']{\bc{A_2, C_1}}$}\label{fig:spiral_inflation_inj2}
    \end{subfigure}
    \begin{subfigure}[b]{.23\linewidth}
    \scalebox{0.8}{\input{../../figures/causal_structures/triangle_structure_injectable_highlight_2}}
    \caption{$\AnSub[\graph]{\bc{A,C}}$}\label{fig:spiral_inflation_iminj2}
    \end{subfigure}
    \caption{Some injectable sets $\Inj[\graph]{\graph'}$ of the Spiral inflation ($\graph'$) and their corresponding images $\ImInj[\graph]{\graph'}$ in the Triangle structure ($\graph$).}
    \label{fig:injectablesets}
    \end{figure}
    \end{nscenter}
    % \begin{definition}
    %     Given a causal structure $\graph$ and an inflation $\graph'$ of $\graph$, define the \term{injectable sets} in $\graph'$ and the \term{images of the injectable sets} in $\graph$, (respectively denoted $\Inj[\graph]{\graph'}$ and $\ImInj[\graph]{\graph'}$), as follows:
    %     \begin{align*}
    %         \Inj[\graph]{\graph'} &\defined \bc{N' \subseteq \nodes' \mid \exists N \subseteq \nodes : \AnSub[\graph']{N'} \sim \AnSub[\graph]{N}} \\
    %         \ImInj[\graph]{\graph'} &\defined \bc{N \subseteq \nodes \mid \exists N' \subseteq \nodes' : \AnSub[\graph']{N'} \sim \AnSub[\graph]{N}}
    %     \end{align*}
    % \end{definition}

    % \begin{lemma}
    %     \label[lemma]{lem:inflation}
    %     \term{The Inflation Lemma}~\cite[Lemma 3]{Inflation} Given a particular inflation $\graph'$ of $\graph$ and a marginal model $\prob^{\ImInj[\graph]{\graph'}}$ compatible with $\graph$ then all marginal models $\prob^{\Inj[\graph]{\graph'}}$ are compatible with $\graph'$ provided that $\prob[N] = \prob[N']$ for all instances where $N \sim N'$.
    % \end{lemma}

    % \begin{proof}
    %     Given that $\prob^{\ImInj[\graph]{\graph'}}$ is compatible with $\graph$, it admits a joint distribution $\prob[\nodes]$ that can be factorized into its causal parameters $\prob[\nodes] = \prod_{n \in \nodes} \prob[n\mid \Pa[\graph]{n}]$. Given \cref{eq:inflation_defn}, one can create a set of \textit{inflated} causal parameters by matching causal parameters according to respective copy-indices: $\forall n' \in \nodes' : \prob[n'\mid \Pa[\graph']{n'}] \defined \prob[n\mid \Pa[\graph]{n}]$. This uniquely induces a compatible joint distribution $\prob[\nodes']$ on $\graph'$\footnote{Of course, there exists compatible joint distributions on $\nodes'$ that can not be constructed in this manner. The claim is that all joint distributions that are constructed in this way are compatible.}: $\prob[\nodes'] = \prod_{n' \in \nodes'} \prob[n'\mid \Pa[\graph']{n'}]$. The proof is completed by demonstrating that the marginals of $\prob[\nodes']$ are members of the marginal model $\prob^{\Inj[\graph]{\graph'}}$ provided that $\prob[N] = \prob[N']$ for all instances where $N \sim N'$. Given $N' \in \Inj[\graph]{\graph'}$ and $N \sim N'$:
    %     \[ \sum_{\nodes' \setminus N'} \prob[\nodes'] = \sum_{\nodes' \setminus N'} \prod_{n' \in \nodes'} \prob[n'\mid \Pa[\graph']{n'}] = \prod_{n' \in N'} \prob[n'\mid \Pa[\graph]{n'}] = \prod_{n \in N} \prob[n\mid \Pa[\graph]{n}] = \prob[N] = \prob[N']  \]
    % \end{proof}
